\documentclass[letterpaper]{article}
\usepackage[submission]{aaai2027}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\urlstyle{rm}
\def\UrlFont{\rm}
\usepackage{natbib}
\usepackage{caption}
\frenchspacing
\usepackage{booktabs}
\usepackage{amsmath}
\pdfinfo{/TemplateVersion (2027.1)}
\setcounter{secnumdepth}{0}

\newcommand{\sys}{\textsc{ReproBench}}
\newcommand{\bof}{\textsc{BOF}}
\newcommand{\cmdi}{\textsc{CMDI}}
\newcommand{\auth}{\textsc{AuthBypass}}

\title{ReproBench: Benchmarking LLM Agents on From-Scratch IoT Firmware Vulnerability Reproduction}
\author{Anonymous Submission}
\affiliations{}

\begin{document}
\maketitle

\begin{abstract}
Large language model (LLM) agents are increasingly evaluated on cybersecurity tasks, yet most benchmarks begin after the target environment has already been prepared: the agent receives source code, a patch, a running service, a container, or an executable binary. This setting leaves open a central question for real-world vulnerability analysis: can an agent reconstruct the missing environment needed to reproduce a known vulnerability from scratch? We introduce \sys, a public-evidence-grounded benchmark for from-scratch reproduction attempts of IoT firmware vulnerabilities from only a CVE identifier. \sys{} contains 30 manually curated IoT CVEs, balanced across buffer overflows, command injections, and authentication bypasses. Each task is accompanied by a manually inspected public-evidence dossier built from CVE records, NVD entries, vendor advisories, public PoCs, exploit databases, blogs, and firmware references. Agents must traverse a six-stage vulnerability reproduction pipeline: information gathering, firmware acquisition, firmware extraction, binary identification, service rehosting, and vulnerability triggering. We propose an evidence-grounded, non-binary scoring framework that separately evaluates planning and execution and requires observable artifacts for every non-zero score. Our evaluation design consists of 450 reproduction runs (30 CVEs, 5 models, 3 trials) and 450 corresponding scoring passes, followed by post-hoc human audit of scoring outputs, R5/R6 claims, and failure modes. \sys{} measures whether agents can progressively perform vulnerability reproduction and produce auditable real-target evidence rather than merely final claims, exposing the gap between textual vulnerability understanding and grounded firmware execution.
\end{abstract}

\input{sections/100-introduction}
\input{sections/200-motivation-and-task}
\input{sections/300-benchmark-construction}
\input{sections/400-evidence-grounded-scoring}
\input{sections/500-experimental-design}
\input{sections/600-evaluation-results}
\input{sections/700-failure-modes}
\input{sections/800-discussion}
\input{sections/900-related-work}
\input{sections/1000-conclusion}

\bibliography{aaai2027}

\end{document}
