\section{Introduction}

%% 现有benchmark假设目标环境已准备好，真实漏洞复现从CVE起步更困难
%
LLM agents now plan, call tools, write code, and operate inside software repositories with growing autonomy~\cite{swebench,programbench}. 
%
This shift has prompted a wave of benchmarks measuring agentic performance on software engineering and cybersecurity tasks, from issue resolution~\cite{swebench} and program rewriting~\cite{programbench} to vulnerability reproduction~\cite{cybergym,krepro}, exploitation~\cite{cvebench,exploitgym,exploitbench}, and offense--defense exercises~\cite{bountybench,secbench}. 
%
A common assumption underlies all of them: the target environment has already been prepared. 

%
Specifically, the agent receives a repository, a patch, a sanitizer-instrumented binary, a running Docker, and then is scored on what it does \emph{after} that starting line. 
%
In real-world vulnerability analysis, however, a typical investigation usually begins with a bare identifier---a CVE number, which is followed by identifying the affected product, locating the correct artifact, recovering a runnable environment, and validating the vulnerability by producing a proof-of-concept (PoC). 
%
We call the prepared setting \emph{post-environment} evaluation and the from-scratch setting \emph{pre-environment} evaluation. 
%
The gap between them is not cosmetic: it is the gap between grading an exploit and grading the ability to reach a target worth exploiting.


We focus on a domain where this gap is especially sharp: IoT firmware vulnerability reproduction. 
%
A firmware image is a proprietary binary blob compiled for MIPS or ARM, packed in vendor-specific formats, dependent on missing NVRAM state and shared libraries, and reachable only after \textit{rehosting} under architecture-level emulation.
%
Unlike source-level targets, firmware cannot be rebuilt from a patch; the analyst must obtain the exact image, extract it from a vendor archive, identify the vulnerable binary among dozens of blobs, and rehost the service on a synthetic environment before any exploit can be triggered. 
%
This makes firmware reproduction an end-to-end artifact reconstruction and validation task, where failure can occur at every step and where a polished-looking PoC may never touch the real target. 
%
%The security stakes are concrete: IoT devices are deployed at billions of units %across homes, factories, and edge infrastructure, and the same opacity that %makes firmware hard to rehost also makes it a persistent reservoir of unpatched, %remotely exploitable bugs.

%% 引入ReproBench：从CVE ID出发评估完整artifact-to-execution pipeline
To address this gap, we introduce \sys, a benchmark that evaluates whether LLM agents can move from a bare CVE identifier toward auditable evidence of IoT firmware vulnerability reproduction.
%
\sys{} deliberately withholds the prepared environment and scores the full artifact-to-execution pipeline. 
%
In doing so, it stresses capabilities that existing benchmarks do not exercise at all: open-world information gathering, artifact provenance checking, cross-architecture binary analysis, long-horizon tool orchestration, and grounded validation against the real target rather than against a surrogate of the agent's own construction.

\begin{table*}[t]
    \centering
    \caption{Comparison with representative benchmarks. All existing work operates post-environment. \sys{} is the only benchmark where environment construction is the scored task itself (pre-environment), targeting IoT firmware.}
    \label{tab:compare}
    \small
    \begin{tabular}{lclll}
    \toprule
    \textbf{Benchmark} & \textbf{From Scratch} & \textbf{Input} & \textbf{Task Type} & \textbf{Pre/Post-Env.} \\
    \midrule
    SWE-bench~\cite{swebench} & \textcolor{red}{\ding{55}} & Source Code & Issue Resolution & Post \\
    ProgramBench~\cite{programbench} & \textcolor{green}{\ding{51}} & Binary Program & Program Rewrite & Post \\
    CyberGym~\cite{cybergym} & \textcolor{red}{\ding{55}}  & Source code & Vulnerability Reproduction & Post \\
    CVE-Bench~\cite{cvebench} & \textcolor{red}{\ding{55}}  & Source code & Vulnerability Exploitation & Post \\
    ExploitBench~\cite{exploitbench} & \textcolor{red}{\ding{55}}  & Binary Program & Vulnerability Exploitation & Post \\
    ExploitGym~\cite{exploitgym} & \textcolor{red}{\ding{55}}  & Binary Program & Vulnerability Exploitation & Post \\
    K-Repro~\cite{krepro} & \textcolor{red}{\ding{55}}  & Source Code & Vulnerability Reproduction & Post \\
    BountyBench~\cite{bountybench} & \textcolor{red}{\ding{55}}  & Source Code & Offense \& Defense & Post \\
    SEC-Bench~\cite{secbench} & \textcolor{red}{\ding{55}}  & Source Code & PoC gen.\ \& Patching & Post \\ \hline
    \textbf{\sys{} (Ours)} & \textcolor{green}{\textbf{\ding{51}}} & \textbf{CVE Identifier} & \textbf{Vulnerability Reproduction} & \textbf{Pre} \\
    \bottomrule
    \end{tabular}
\end{table*}

Our evaluation exposes a failure behavior that, to our knowledge, has not been isolated in prior benchmarking: when rehosting becomes difficult, agents do not report failure---they \emph{substitute}. 
%
They produce Python mock servers or synthetic C harnesses that crash in the expected way, and wrap them in coherent reports with valid exploit syntax and convincing crash traces. 
%
In short, the vulnerability is being emulated, but the environment is not. 
%
\sys{} addresses this with non-binary, evidence-grounded scoring that decomposes reproduction into six phases and applies explicit real-target gating at the rehosting and triggering phases, so that a simulated reproduction can be detected. 
%
%Across 450 runs, 69.8\% exhibit simulation substitution, while only 4.7\% of %CVE--model pairs achieve real-target vulnerability triggering---a distinction %that binary, post-environment scoring would erase entirely.


Our contributions are as follows:
\begin{itemize}

\item We formulate \emph{CVE-only} vulnerability reproduction as a from-scratch, long-horizon LLM agent task, and introduce the pre/post-environment distinction that separates \sys{} from all prior cybersecurity benchmarks.

\item We carefully construct, from official CVE database, a 30-CVE public-evidence dataset balanced across buffer overflow, command injection, and authentication bypass, reported between 2020 to 2026..

\item We propose an evidence-grounded, non-binary scoring framework that decomposes reproduction into six phases with real-target gating, jointly measuring planning and execution, rejecting simulated reproductions.

\item We evaluate 450 reproduction runs (30 CVEs, 5 models, 3 trials) and find a dominant, previously unreported failure mode---\emph{simulation substitution} (69.8\% of runs)---showing that real-target triggering remains near-insurmountable (4.7\%).

\end{itemize}

