\section{Background and Pre-Environment}
\label{sec:related}

\begin{table*}[t]
    \centering
    \caption{Comparison with representative benchmarks. All existing work operates post-environment. \sys{} is the only benchmark where environment construction is the scored task itself (pre-environment), targeting IoT firmware.}
    \label{tab:compare}
    \small
    \begin{tabular}{lclll}
    \toprule
    \textbf{Benchmark} & \textbf{From Scratch} & \textbf{Input} & \textbf{Task Type} & \textbf{Pre/Post-Env.} \\
    \midrule
    SWE-bench~\cite{swebench} & \textcolor{red}{\ding{55}} & Source Code & Issue Resolution & Post \\
    ProgramBench~\cite{programbench} & \textcolor{green}{\ding{51}} & Binary Program & Program Rewrite & Post \\
    CyberGym~\cite{cybergym} & \textcolor{red}{\ding{55}}  & Source code & Vulnerability Reproduction & Post \\
    CVE-Bench~\cite{cvebench} & \textcolor{red}{\ding{55}}  & Source code & Vulnerability Exploitation & Post \\
    ExploitBench~\cite{exploitbench} & \textcolor{red}{\ding{55}}  & Binary Program & Vulnerability Exploitation & Post \\
    ExploitGym~\cite{exploitgym} & \textcolor{red}{\ding{55}}  & Binary Program & Vulnerability Exploitation & Post \\
    K-Repro~\cite{krepro} & \textcolor{red}{\ding{55}}  & Source Code & Vulnerability Reproduction & Post \\
    BountyBench~\cite{bountybench} & \textcolor{red}{\ding{55}}  & Source Code & Offense \& Defense & Post \\
    SEC-Bench~\cite{secbench} & \textcolor{red}{\ding{55}}  & Source Code & PoC gen.\ \& Patching & Post \\ \hline
    \textbf{\sys{} (Ours)} & \textcolor{green}{\textbf{\ding{51}}} & \textbf{CVE Identifier} & \textbf{Vulnerability Reproduction} & \textbf{Pre} \\
    \bottomrule
    \end{tabular}
\end{table*}

% 软件工程benchmark
\subsection{Software Engineering Benchmarks}
SWE-bench~\cite{swebench} is the first work aiming to evaluate whether large language models can resolve real-world GitHub issues by producing patches against a pre-checked-out repository snapshot; success is judged by the project's own test suite. SWE-bench-Live extends this with a live-updatable, contamination-resistant pipeline but still hands the agent a ready container. ProgramBench~\cite{programbench} shares our from-scratch philosophy: the agent receives only a compiled executable and documentation, and must reconstruct a behaviorally-equivalent program. However, it operates on user-space software with readable documentation, not on closed-source vendor firmware with no build system.

% 安全benchmark
\subsection{Cybersecurity Benchmarks}
CyberGym~\cite{cybergym} provides 1{,}507 instances from OSS-Fuzz projects with pre-built sanitizer-instrumented executables and a containerized PoC submission interface; its successor CyberGym-E2E~\cite{cybergyme2e} extends to end-to-end discover$\rightarrow$PoC$\rightarrow$patch but still places the agent inside a pre-configured build environment. CVE-Bench~\cite{cvebench} ships 40 critical web-application CVEs as running Docker-Compose stacks; the agent's task is to exploit a pre-deployed service. ExploitBench~\cite{exploitbench} measures exploitation depth on V8 N-day bugs with pre-built binaries, patch diffs, and a deterministic 16-flag capability bitmap. ExploitGym~\cite{exploitgym} tasks agents with escalating a given proof-of-vulnerability input into a full exploit, again with ready-built targets. K-Repro~\cite{krepro} studies Linux kernel N-day reproduction from a patch commit, operating inside a prepared QEMU VM with KASAN. BountyBench~\cite{bountybench} evaluates offense and defense on 25 real OSS systems, each manually packaged into Docker containers. SEC-Bench~\cite{secbench} automates CVE instance construction with verifiable PoCs but still delivers each task as a pre-built Docker image.

% 对比表
Table~\ref{tab:compare} summarizes the key differences along three dimensions: what the agent receives as input, whether the environment is pre-prepared, and what type of target the agent operates on. Every existing benchmark provides the agent with a prepared environment and evaluates post-environment capabilities. None targets IoT firmware, which requires cross-architecture rehosting of closed-source vendor binaries.



% 最后一段：指出gap，引出ReproBench
\subsection{The Pre-Environment Gap}
All benchmarks above are \emph{post-environment}: they evaluate what an agent can do \emph{after} the vulnerable target is already built, containerized, or running. None tests whether the agent can \emph{construct} the reproduction environment from scratch---locate the correct firmware image from a bare CVE identifier, unpack vendor-specific formats, identify the vulnerable binary, and rehost the real service under emulation. This pre-environment pipeline is exactly what a security analyst performs in the wild, and it is where agents lose grounding most often: our results show that 69.8\% of runs substitute simulated reproductions for real firmware execution, a failure mode invisible under post-environment evaluation. \sys{} fills this gap by making environment construction the scored task itself, with the scoring skill decomposing reproduction into six phases and applying real-target gating that rejects simulated reproductions.
