\section{Experimental Design}
\subsection{Agent Execution}
\label{sec:agent-runs}
% agent执行：统一prompt，opencode agent，5模型×3次=450 runs
Each agent receives the following prompt (with the CVE identifier substituted accordingly):

\begin{quote}
\small\ttfamily
Reproduce CVE-2023-26315 vulnerability following three main steps: \\
Firstly, design a reproduction plan into a markdown file, named plan.md \\
Secondly, reproduce the vulnerability based on the plan. \\
Finally, conclude the reproduction to a markdown file, named report.md. \\
Note, you must follow 5 rules: \\
Rule-1: *MUST* record the roadblocks that obstacle the reproduction if not strictly along with the plan; \\
Rule-2: *MUST* limit the total cost no more than 5 dollars; \\
Rule-3: *MUST* done in 24 hours; \\
Rule-4: *SHOULD* use sudo password 000000 to install or create anything you need; \\
Rule-5: *MUST* produce, generate, download, write down everything in '/output' directory not in other places, e.g., '/tmp'.
\end{quote}

We use OpenCode as the unified agent harness for all models. Five model configurations are evaluated: \texttt{claude-sonnet-4-6}, \texttt{deepseek-v4-flash-free}, \texttt{glm-5.2}, \texttt{gpt-5.5}, and \texttt{mimo-v2.5-free}. Each model is tested on all 30 CVEs with three independent trials, producing 450 reproduction runs. For each run, we record two types of artifacts: (1) \emph{trace}---session messages and container logs capturing the agent's reasoning and execution process, and (2) \emph{workspace}---all files produced in the \texttt{/output} directory, including the plan, downloaded firmware, extracted filesystems, scripts, logs, and the final report.

\subsection{Scoring Protocol}
% best-of-three排名方式
Every run is evaluated by the scoring skill, producing 450 JSON score files and summaries. For each CVE--model pair, we report the best plan score and the best task score across three trials (may come from different runs), combined as $\text{Overall} = 0.2 \times \text{BestPlan} + 0.8 \times \text{BestTask}$. This reflects the practical question: given multiple attempts, can an agent reproduce a vulnerability at least once? We also report failure attribution based on all 450 runs.

\subsection{Research Questions}

We set six research questions to drive our evaluation:
\begin{itemize}
\item RQ1: How far can agents progress from a CVE id toward reproduction?
\item RQ2: Which stages account for most failures?
\item RQ3: Does plan quality predict execution progress?
\item RQ4: How often do agents produce plausible but invalid artifacts?
\item RQ5: How do vulnerability classes and models affect progress?
\item RQ6: Does evidence-grounded scoring reveal distinctions hidden by binary success?
\end{itemize}
