\subsection{Overall Progress}
% RQ1: agent能进展多远——max-based平均51.1，glm-5.2最强，P5/R6几乎不可达
Table~\ref{tab:model-results} reports the best-of-three results for each model across 30 CVEs. \texttt{glm-5.2} achieves the highest average overall score (64.6/100), followed by \texttt{mimo-v2.5-free} (52.9) and \texttt{claude-sonnet-4-6} (50.0). While real-target success remains rare---only 11 out of 150 CVE--model pairs achieve near-full P5 credit ($\geq$15/20), of which 8 also achieve near-full P6 credit---the best single run reaches 99.0/100, demonstrating that full autonomous reproduction is achievable under favorable conditions.


% 成功案例分析：同架构设备可chroot，跨架构几乎不可行
Specifically, five CVEs achieve full or near-full reproduction (overall $\geq$90), which share a common reason: the target devices use ARM64 processors, allowing agents to run the real firmware binary via \textit{chroot} without cross-architecture emulation. In contrast, MIPS-based devices requiring QEMU emulation almost universally fail at P5, because agents cannot reliably configure NVRAM, shared libraries, and network bridges.


Notably, the leading model, \texttt{glm-5.2}, wins not through raw reasoning but through task-appropriate behavior. It averages 11.5/15 on P2 (Firmware Acquisition) under best-of-three scoring, well above \texttt{claude-sonnet-4-6}'s 7.7/15; since P2 gates all downstream phases, this gap cascades---\texttt{claude-sonnet-4-6} has 20 runs where the plan exceeds 50 yet the task stalls below 15, all blocked at P2. \texttt{glm-5.2} also achieves the strongest fallback planning (32.2/100 vs.\ 15.0--28.6 for the others), which correlates with deeper pipeline progression. On from-scratch reproduction, persistence in artifact acquisition and fallback-driven recovery matter more than model size.
