\subsection{Phase-Specific Capability (PSC)}
%%% RQ6: graded评分揭示二元评分隐藏的差异
%%While 143/150 pairs (95.3\%) would be failures under binary %%evaluation, graded scoring reveals a 23.5-point spread (41.7--65.%%2). Best-of-three scoring adds $\sim$10 points over per-run %%averages, with stronger models showing larger variance (e.g., %%\texttt{glm-5.2}: +14.3), suggesting that succeeding at least once %%is itself a capability dimension.
%%

% 异常点分析：18个CVE存在分化，graded评分暴露阶段特定能力
To quantify what capabilities binary metrics conceal, we conduct an anomaly analysis across all 450 runs. We define a divergence point where a minority of runs score $\geq$40\% of the phase maximum while a majority score $\leq$15\%. These two thresholds are chosen to separate genuine capability from attempt-score noise, which caps at $\sim$7\%. For each CVE we select the earliest divergent phase to avoid cascading low scores from unmet prerequisites. We identify \textit{18 CVEs} exhibiting such divergence and inspect the HIGH and LOW runs' artifacts and trajectories for each. Finally, we conclude the following three phase-specific capabilities.

% 三大分化模式：阶段特定能力
\noindent{\textbf{PSC 1: Search Strategy.}} The first bottleneck is whether the agent verifies the assumption that firmware is unavailable. HIGH runs test the ``firmware unavailable'' hypothesis by issuing real \texttt{curl} requests to vendor CDNs, regional sites, and community firmware archives; LOW runs accept the hypothesis without verification and jump to simulation. On CVE-2020-14140, only one of 15 runs actually curls the Xiaomi CDN, discovers the firmware is publicly downloadable, and statically analyzes the extracted Lua controllers; the other 14 runs assume unavailability and produce Python mock servers with zero \texttt{curl} invocations.

\noindent{\textbf{PSC 2: Tooling Knowledge.}} When firmware is encrypted in a vendor-proprietary format, standard \texttt{binwalk} fails and the agent must identify the correct decryption tool. HIGH runs possess domain-specific tooling knowledge to handle encrypted firmware---the \texttt{delink} tool for D-Link MH01 encryption, OpenWrt GPL code for deriving the DIR-X3260 AES key, or BigNerd95's GSFW.py for Grandstream firmware---while LOW runs assume standard \texttt{binwalk -e} suffices and produce empty extraction directories. On CVE-2024-6045, only 4/15 runs know the \texttt{delink} Rust tool is required; LOW runs create \texttt{firmware/} and \texttt{extracted/} directories that remain empty because standard binwalk cannot process MH01 encryption.

\noindent{\textbf{PSC 3: Rehosting Technique.}} Even when the correct binary is extracted, proprietary firmware services fail under QEMU due to missing NVRAM state, kernel ioctl dependencies, and non-standard FastCGI interfaces. HIGH runs author custom \texttt{-nostdlib} LD\_PRELOAD ioctl shims, NVRAM stub libraries, and FastCGI launchers to satisfy proprietary binary dependencies under QEMU; LOW runs hit QEMU failures and switch to C/Python reimplementation of the vulnerability pattern. On CVE-2020-13389, the top-scoring run (\texttt{glm-5.2}, 19/20) writes a 13-line ioctl shim that fakes \texttt{SIOCGIFADDR} responses for the \texttt{br0} interface, allowing the real Tenda httpd to reach \texttt{bind}/\texttt{listen}; a \texttt{claude-sonnet-4-6} LOW run spins in an infinite ioctl/nanosleep retry loop and never binds.

Under binary evaluation, all 18 divergent CVEs would be uniformly labeled as failures, yet the HIGH runs demonstrate distinct capabilities---hypothesis verification, tool-chain selection, and environment engineering---that are directly transferable to real-world vulnerability analysis but invisible without graded, phase-level scoring.

% HIGH run的三个共同特质
% Across all three patterns, HIGH runs share three common traits: (1) authoring shim code (libnvram/libwrscfg/nofork stubs, FastCGI launchers, ioctl hooks) that makes proprietary binaries runnable under QEMU; (2) distinguishing flashable firmware binaries from GPL source packages, which lack runtime shared libraries such as \texttt{ld-uClibc.so.0}; and (3) trying multiple URLs---regional pages, static CDNs, community archives---rather than abandoning acquisition after the first 404. These traits are invisible under binary evaluation, which collapses all 18 divergent CVEs into uniform failures.


% \begin{mdframed}[linecolor=black,linewidth=1pt,backgroundcolor=gray!10,roundcorner=3pt,nobreak=true]
% \noindent\textbf{Result-2:} Evidence-grounded scoring reveals distinctions hidden by binary success. Anomaly analysis exposes three phase-specific capabilities that can pass through the bottlenecks.
% \end{mdframed}