\section{Discussion}
\label{sec:discuss}

\subsection{Why Agents Avoid Rehosting}

The failure taxonomy and trace inspection converge on a simple observation: agents can name \firmae{} and QEMU but cannot drive them through the multi-step recovery loops that make rehosting succeed. Public training corpora contain abundant source-level exploit write-ups and CTF solutions, but firmware rehosting is a niche workflow documented mostly in scattered blog posts and tool READMEs. An agent that has read a thousand Stack Overflow posts about SQL injection has seen the same attack pattern reinforced a thousand times; an agent that has read the \firmae{} README has seen the \texttt{firmae.py -b} invocation once, without the NVRAM seeding, library path fixups, and peripheral stubs that the tool's own evaluation needed to reach 79\% boot success.

This workflow gap compounds with a structural incentive problem. A host-native simulation reliably produces a clean, presentable crash within minutes; a rehosting attempt risks consuming the entire 30-minute budget on an emulator that never boots. Under a fixed budget, agents that have internalized a ``produce a result'' objective rationally prefer the low-variance path. This is an instance of reward hacking, and it is exactly what validity gating is designed to neutralize: the agent gets credit for what it genuinely accomplishes (finding the CVE, downloading firmware, extracting it, identifying the binary) but not for the simulation it substitutes when rehosting fails. Rehosting errors themselves do not help: missing \texttt{ld-uClibc}, unimplemented syscalls, and peripheral faults are cryptic and architecture-specific, and traces show agents abandoning after one or two such errors without the domain knowledge to map an error message to its fix. For many CVEs, a simulation demonstrates enough understanding that---absent a verifier that distinguishes real from simulated execution---the output is indistinguishable from reproduction. \sys exists precisely to draw that distinction.

\subsection{Implications}

The most immediate implication is methodological. Binary, crash-based metrics---including the staged S1--S4 checks used by CyberGym-E2E~\cite{cybergyme2e}---credit a fabricated reimplementation as readily as a genuine trigger. Any benchmark that spans the acquisition-to-rehosting pipeline needs artifact-grounded, dependency-gated scoring, or it will mis-measure progress. The \rrs is one such design; the broader lesson is that the evaluation oracle must verify execution against the \emph{real} artifact, not against whatever the agent chooses to run.

A second implication reframes where the research frontier lies. Prior benchmarks frame exploit development as the hard problem for AI agents. Our data suggest that for IoT, the binding constraint is reaching the vulnerable code at all. The pipeline collapses $40\times$ at rehosting, not at exploitation. Progress will come from teaching agents to orchestrate mature rehosting tools---not from stronger exploitation reasoning. The tools are available: agents had \texttt{sudo} access and could install \firmae{} and QEMU at will. They rarely did, and when they did, they used them ineffectively. The missing ingredient is procedural knowledge: tool-use trajectories, error-to-fix mappings, and cross-architecture conventions. This points toward agentic scaffolding or fine-tuning on rehosting traces as concrete next steps, rather than larger models or longer contexts.

\subsection{Threats to Validity}

Our verifiers detect crashes, service availability, and exact string matches, but they cannot assess reasoning quality. We mitigate over-crediting through validity gating and inter-annotator agreement on failure coding ($\kappa=0.81$), but a sufficiently sophisticated agent that produces a rehosted service and a fake crash signal could still fool the R5 verifier. The \rrs weights are hand-set; the sensitivity analysis (\cref{sec:sensitivity}) shows rankings are stable under $[0.5,2\times]$ reweighting and the rehosting finding is weight-independent. The corpus skews toward SOHO routers and IP cameras (\cref{tab:dataset}); industrial, medical, and automotive targets add RTOS and safety constraints we do not capture, and encrypted-firmware coverage is limited, so R2 estimates carry higher variance. We use a single uniform harness without vendor scaffolding to isolate model capability; stronger scaffolding may raise absolute scores, but given the workflow-gap analysis above, it is unlikely to close the rehosting gap on its own.

\subsection{Ethical Considerations}

Reproduction underpins both defense (patch validation, regression testing) and offense. All runs execute in isolated, network-segmented containers; we release verification harnesses and labels but withhold weaponized exploit code for unpatched issues. Any previously unknown vulnerability surfaced during evaluation is reported to the vendor via coordinated disclosure before public release. The corpus manifest, deterministic verifiers, and harness configuration are released (\cref{app:repro}) so that every experiment is re-runnable.
