\section{Discussion}
\subsection{What \sys{} Measures}
\sys{} does not claim that every CVE has a prebuilt, author-executed oracle. Instead, it evaluates whether agents can produce auditable evidence aligned with public vulnerability facts and real firmware artifacts. This is a deliberate design choice. From-scratch reproduction often begins from incomplete public information, and constructing a fully executable oracle for every IoT firmware CVE would itself require substantial expert effort. \sys{} measures the agent's ability to transform public evidence into concrete artifacts and real-target evidence under a uniform protocol.

\subsection{Implications for Agent Evaluation}
Prepared environments can hide a major class of agent failures. An agent that succeeds when given a running service may still fail when asked to recover the service from a public vulnerability identifier. Future benchmarks for long-horizon agents should record traces and workspaces, require artifact provenance, distinguish public-evidence insufficiency from agent error, and reject substitutions that do not preserve task validity.

\subsection{Implications for Agent Design}
The benchmark targets recovery-oriented tool use, not only vulnerability knowledge. Firmware reproduction requires error-to-fix mappings, persistent artifact tracking, architecture-aware execution, and self-checks that distinguish real targets from simulations. Rehosting scaffolds may improve absolute performance, but the benchmark should continue to measure whether agents preserve the real-target requirement.

\subsection{Limitations and Ethics}
The dataset is manually balanced across three vulnerability classes and is not intended to match the natural distribution of IoT CVEs. Public-evidence dossiers may contain incomplete or stale information; we mitigate this by requiring explicit evidence for scoring, preserving failure attribution, and auditing scoring outputs after the experiments. The scoring skill is not a deterministic exploit oracle, so human analysis is used to check evidence consistency and adjudicate ambiguous R5/R6 claims. Ethically, \sys{} targets defensive reproduction, patch validation, and agent evaluation. Experiments are conducted in isolated workspaces, and real-target credit requires controlled evidence rather than weaponized exploitation.
